|

### 2025-01-26 doc/paper.qmd
done

Building on this foundation, the original study by @ball_how_2008 investigates the extent to which quarterly earnings announcements contribute new information to the market, assessing their role in shaping annual share price movements. By estimating the R² from regressions of annual stock returns on earnings announcement window returns, the paper quantifies the informativeness of earnings releases, finding that they account for only 1% to 2% of total annual volatility. This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting, reinforcing prior market expectations rather than acting as a primary source of new insights. The study further documents an increasing trend in earnings informativeness in recent years, potentially linked to regulatory changes, shifts in analyst activity, or broader market conditions.

@@

# Task 1 - Replication of Key Tables and Figures {#sec-task1}

Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results. This ensures alignment with the original findings before extending the analysis in later tasks. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period. The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations.

-----
##The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.

##@fig-market-shares illustrates the market shares of audit firms — Big 4, CR4, and 10KAP — for the number of PIE statutory audits conducted in 2021. Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report. The discussion of replication findings is presented in @sec-results.
```{python}
#| label: fig-market-shares
#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
#| fig-align: center
#| echo: false

@@

@@

1. Based on the original paper, I do not gather analyst expectations or estimate earnings deviations for my replication. Instead, I only require stock return data and earnings announcement dates, which simplifies the data collection process.

2. Following @ball_how_2008, I define earnings announcement windows as the three-day period surrounding the earnings release (-1 to +1), where Day -1 is the last trading day before the announcement, Day 0 is the announcement day, and Day +1 is the first trading day after the announcement. According to @center_for_research_in_security_prices_crsp_crsp_2024 guide, data are never provided on weekends or trading holidays, meaning there is no need for manual filtering of such days. However, if an earnings announcement falls on a non-trading day, adjustments are necessary to maintain the three-day window. Hence, earnings announcement dates are first extracted from Compustat and then matched with CRSP trading data to obtain stock returns for the event window (-1, 0, +1). If Day 0 falls on a weekend or holiday, it is shifted to the next available trading day. Similarly, if Day -1 or Day +1 is unavailable due to a non-trading day, the nearest prior or next trading day, respectively, is used to preserve the event window. This adjustment prevents shortening the window, ensuring a complete three-day period for capturing the full market response to earnings announcements.

3. Same as @ball_how_2008, I group earnings announcements based on their actual announcement dates rather than the fiscal periods they cover. Since Compustat provides the precise earnings announcement date and CRSP aligns stock returns with trading days, this approach ensures consistency with the original study. No further adjustments are needed to realign quarters.

4. As in the original paper, firm-years are selected based on available stock return data in CRSP. While @ball_how_2008 restrict the sample to firms with at least 240 trading days per year, I follow the course guidance and do not apply this restriction, allowing for a slightly larger sample size. This adjustment should be considered when interpreting differences from the original study.

By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels) from @ball_how_2008. A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.

@@

1.	The original report references the reports prepared by national competent authorities (NCAs) responsible for audit oversight as the main source of data, where the data refers to the years 2020 and 2021 and was collected in 2022 [@EC_Report_2024, p.1]. However, this replication uses data obtained from the Audit Analytics Transparency Reports database via WRDS, which provides the latest available version as of September 2024, updated quarterly [@WRDS_Audit_Analytics_Transparency_Reports]. Due to potential adjustments and updates made to the database since the original data collection period, there may be differences that could affect the results. For example, audit firms may disclose updated information in subsequent reports, which would be reflected in the later database version rather than the historical snapshot used in the original report. Furthermore, the data vendor regularly updates its databases to correct errors and add new information, which may be included in the later data but not in the 2022 snapshot.
2.	The original paper outlines key terms that will be used in this project to ensure consistency and accuracy in the replication. @EC_Report_2024 defines the 'Big Four' as Deloitte, EY, KPMG, and PwC; the 'CR4' as the four largest audit firms in each country; and the '10KAP' as a group consisting of Baker Tilly, BDO, Deloitte, EY, Grant Thornton, KPMG, Mazars, Nexia, RSM, and PwC. 
3.	As for the geographical scope, I use the variable `trans_report_auditor_state` to identify the country associated with each audit firm rather than the audited company’s headquarter country (`headquarter_country` variable). Since the objective is to analyze audit market concentration and the market share of audit firms within specific countries, the country of the audit firm’s reported activity is more relevant than the headquarter country of the entities they audit.
4.	Another potential source of discrepancies between the original and replicated tables may be the choice of variables pulled from Audit Analytics. For example, in the `audit_europe.feed76_transparency_reports` table, I chose `entity_map_fkey` over `entity_map_key`, as this unique identifier is created by WRDS for merging [@WRDS_Audit_Analytics_Transparency_Reports]. Since the report does not specify the choice of variables used from the database, this could cause differences in the results.
5.	For the purpose of replicating Figure 3, I use the `report_year` variable as the primary filter to define the relevant data for year 2021. This choice is based on the fact that `report_year` represents the idealized fiscal year of the Transparency Report, based on the *Europe Transparency Reports Data Dictionary* by Wharton Research Data Services [-@Europe_Transparency_Reports_Data_Dictionary], which aligns directly with the year-based aggregation needed for Figure 3. While the `report_period_end_date` provides the exact end date of each reporting period [@Europe_Transparency_Reports_Data_Dictionary], using `report_year` allows for a consistent, annual aggregation without requiring additional alignment of various period end dates. This approach simplifies the data extraction and ensures that all entries correspond to the fiscal year 2021.

## Replication Steps {#sec-replication_steps1}

##The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures. For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

##The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis. The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].

Step 1: Pulling the Data and Managing the Database
This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

@@

Step 2: Data Preparation
The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021. To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.

@@

Step 3: Analysis Implementation and Figure Reproduction
The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data. The analysis begins by calculating the market shares of the Big 4, 10KAP, and CR4 audit firm groups for the number of statutory audits conducted in 2021. For each country, the Big 4 market share is derived as the percentage of PIE statutory audits conducted by Deloitte, EY, KPMG, and PwC, while the CR4 market share represents the top four audit firms in each country based on audit counts. The 10KAP market share includes the Big 4 along with six additional networks, providing a broader view of market concentration.

@@

## Results {#sec-results1}
Comparing our replication results of Figure 1 (see Figure ## below) with those in the original report (see Figure 1 below) reveals both similarities and discrepancies.

@@

@@

In summary, the replication effectively captures the original report's key findings, confirming the dominance of the Big 4 and the broader 10KAP group in the European audit market. The analysis highlights varying degrees of market concentration across countries, with some demonstrating a more decentralized audit landscape. While discrepancies in individual country results, such as Romania, underline the importance of methodological alignment, the strong similarity between the overall market shares reported in the original report and the replicated results underscores the robustness and reliability of the findings.

>>>>

Building on this foundation, the original study by @ball_how_2008 investigates the extent to which quarterly earnings announcements contribute new information to the market, assessing their role in shaping annual share price movements. By estimating the R² from regressions of annual stock returns on earnings announcement window returns, the paper quantifies the informativeness of earnings releases, finding that they account for only 1% to 2% of total annual volatility. This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting, reinforcing prior market expectations rather than acting as a primary source of new insights. Unlike traditional event studies that assume market efficiency, @ball_how_2008 allow for potential market mispricing by not imposing a unit slope restriction in their regressions, meaning that their approach can capture under- or overreaction to earnings announcements. They also emphasize that extending the event window beyond the earnings announcement period would shift the research focus from earnings “surprise” to broader financial reporting effects, such as its role in debt contracting and executive compensation. The study further documents an increasing trend in earnings informativeness in recent years, potentially linked to regulatory changes, shifts in analyst activity, or broader market conditions.

@@

# Task 1 - Replication of Key Tables and Figures {#sec-task1}
Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results, ensuring alignment with the original findings before extending the analysis in @sec-task2. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period. The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations. The discussion of replication findings is presented in @sec-results1.

@@

Based on the original paper, I do not gather analyst expectations or estimate earnings deviations for my replication. Instead, I only require stock return data and earnings announcement dates, which simplifies the data collection process.

Same as @ball_how_2008, I group earnings announcements based on their actual announcement dates rather than the fiscal periods they cover. Since Compustat provides the precise earnings announcement date and CRSP aligns stock returns with trading days, this approach ensures consistency with the original study. No adjustments are made to realign quarters.

@@

1. Following @ball_how_2008, I define earnings announcement windows as the three-day period surrounding the earnings release (-1 to +1), where Day -1 is the last trading day before the announcement, Day 0 is the announcement day, and Day +1 is the first trading day after the announcement. According to @center_for_research_in_security_prices_crsp_crsp_2024 guide, data are never provided on weekends or trading holidays, meaning there is no need for manual filtering of such days. However, if an earnings announcement falls on a non-trading day, adjustments are necessary to maintain the three-day window. Hence, earnings announcement dates are first extracted from Compustat and then matched with CRSP trading data to obtain stock returns for the event window (-1, 0, +1). If Day 0 falls on a weekend or holiday, it is shifted to the next available trading day. Similarly, if Day -1 or Day +1 is unavailable due to a non-trading day, the nearest prior or next trading day, respectively, is used to preserve the event window. This adjustment prevents shortening the window, ensuring a complete three-day period for capturing the full market response to earnings announcements.

2. As in the original paper, firm-years are selected based on available stock return data in CRSP. While @ball_how_2008 restrict the sample to firms with at least 240 trading days per year, I follow the course guidance and do not apply this restriction, allowing for a slightly larger sample size. This adjustment should be considered when interpreting differences from the original study.

3.

By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated the results from @ball_how_2008. A thorough step-by-step approach, with each step clearly documented, helps to understand and verify the outputs.

@@

1.	The original report references the reports prepared by national competent authorities (NCAs) responsible for audit oversight as the main source of data, where the data refers to the years 2020 and 2021 and was collected in 2022 [@EC_Report_2024, p.1]. However, this replication uses data obtained from the Audit Analytics Transparency Reports database via WRDS, which provides the latest available version as of September 2024, updated quarterly [@WRDS_Audit_Analytics_Transparency_Reports]. Due to potential adjustments and updates made to the database since the original data collection period, there may be differences that could affect the results. For example, audit firms may disclose updated information in subsequent reports, which would be reflected in the later database version rather than the historical snapshot used in the original report. Furthermore, the data vendor regularly updates its databases to correct errors and add new information, which may be included in the later data but not in the 2022 snapshot.

5.	For the purpose of replicating Figure 3, I use the `report_year` variable as the primary filter to define the relevant data for year 2021. This choice is based on the fact that `report_year` represents the idealized fiscal year of the Transparency Report, based on the *Europe Transparency Reports Data Dictionary* by Wharton Research Data Services [-@Europe_Transparency_Reports_Data_Dictionary], which aligns directly with the year-based aggregation needed for Figure 3. While the `report_period_end_date` provides the exact end date of each reporting period [@Europe_Transparency_Reports_Data_Dictionary], using `report_year` allows for a consistent, annual aggregation without requiring additional alignment of various period end dates. This approach simplifies the data extraction and ensures that all entries correspond to the fiscal year 2021.
Since the report does not specify the choice of variables used from the database, this could cause differences in the results.

## Replication Steps {#sec-replication_steps1}
The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.

The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures. For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis. The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].

**Step 1: Pulling the Data and Managing the Database**  
This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

@@

**Step 2: Data Preparation**  
The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021. To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.

@@

**Step 3: Analysis Implementation and Reproduction of Tables and Figure**  
The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data. The analysis begins by calculating the market shares of the Big 4, 10KAP, and CR4 audit firm groups for the number of statutory audits conducted in 2021. For each country, the Big 4 market share is derived as the percentage of PIE statutory audits conducted by Deloitte, EY, KPMG, and PwC, while the CR4 market share represents the top four audit firms in each country based on audit counts. The 10KAP market share includes the Big 4 along with six additional networks, providing a broader view of market concentration.

@@

## Results {#sec-results1}
Comparing the replication results of Figure 1 (see @fig-market-shares) with those from @ball_how_2008 (see Figure 1 below) reveals both similarities and discrepancies.

@@

@fig-market-shares illustrates the... Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report. 
```{python}
#| label: fig-market-shares
#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
#| fig-align: center
#| echo: false

@@

In summary, the replication effectively captures the original report's key findings, confirming the dominance of the Big 4 and the broader 10KAP group in the European audit market. The analysis highlights varying degrees of market concentration across countries, with some demonstrating a more decentralized audit landscape. While discrepancies in individual country results, such as Romania, underline the importance of methodological alignment, the strong similarity between the overall market shares reported in the original report and the replicated results underscores the robustness and reliability of the findings.
##we confirm? "The results are consistent with the view that the primary economic role of reported earnings is not to provide timely new information to the share market. By inference, that role lies elsewhere, for example, in settling debt and compensation contracts and in disciplining prior information,including more timely managerial disclosures of information originating in the firm’s accounting system. The comparatively low “surprise” content of earnings announcements is to be expected, for a variety of reasons. By its nature, accounting earnings is low frequency (quarterly), not discretionary (announced every quarter, independent of whether there is substantial new information to report), and primarily backward-looking. Other information, and hence revision in share price, is comparatively high frequency, frequently discretionary (released only when there is substantial information to report), and both forward-looking and backward-looking."
